* uid: A unique identifier for the Zillow property.

Text:

* description: The description of the listing from Zillow.

Categorical:

* city: The lowercase name of a city or town in or surrounding Austin, Texas.
* homeType: The home type (i.e., Single Family, Townhouse, Apartment).
* hasSpa: Boolean indicating if the home has a Spa.

Date:

* yearBuilt: The year the property was built.

Numeric:

* latitude: Latitude of the listing.
* longitude: Longitude of the listing.
* garageSpaces: Number of garage spaces.
* numOfPatioAndPorchFeatures: The number of unique patio and/or porch features in the Zillow listing.
* lotSizeSqFt: The lot size of the property reported in Square Feet. This includes the living area.
* avgSchoolRating: The average school rating of all school types (i.e., Middle, High) in the Zillow listing.
* MedianStudentsPerTeacher: The median students per teacher for all schools in the Zillow listing.
* numOfBathrooms: The number of bathrooms in a property.
* numOfBedrooms: The number of bedrooms in a property.

Target:

* priceRange: The most recent available price at time of data acquisition, binned into price ranges.

```{r}
library(tidyverse)
library(tidymodels)
library(skimr)
library(here)
library(tidytext)
```

```{r}
set.seed(2021)

df <- read_csv(here('data', 'train.csv')) |> 
  mutate(price_num = parse_number(priceRange),
         hi = price_num > 400000)
split <- initial_split(df, strata = "priceRange")

train <- training(split)
```

```{r}
skim(train)
```

```{r}
train |> 
  count(hi)
```

```{r}
plot_prices <- function(df, ...) {
  df |> 
    ggplot(aes(...)) +
    geom_bar(aes(fill = priceRange), position = "fill") +
    coord_flip()
}

plot_price_curves <- function(df, ...) {
  df |> 
    ggplot(aes(...)) +
    geom_density(aes(color = priceRange))
}
```

### Categorical

```{r}
train |> 
  plot_prices(homeType)

train |> 
  count(homeType)
```

Condo and single family are most (and single family is far away the most)

```{r}
train |> 
  plot_prices(city)

train |> 
  count(city)
```

Prices really depend on city, but all cities have very few listings besides Austin

```{r}
train |> 
  count(hasSpa)

train |> 
  plot_prices(hasSpa)
```

Spas are also predictive

### Numeric

```{r}
train |> 
  filter(lotSizeSqFt < 20000) |> 
  plot_price_curves(lotSizeSqFt)

train |> 
  filter(lotSizeSqFt < 20000) |> 
  ggplot(aes(lotSizeSqFt, numOfBedrooms)) +
  geom_jitter(aes(color = priceRange), alpha = 0.5) +
  scale_y_continuous(breaks = 1:10)
```

```{r}
train |>  
  plot_price_curves(yearBuilt)
```

There are cheap houses that were build in the 1980s

```{r}
ggplot(train, aes(numOfBedrooms, numOfBathrooms)) +
  geom_jitter(aes(color = priceRange))
```

No surprises, number of rooms correlates positively with price

```{r}
ggplot(train, aes(longitude, latitude)) +
  geom_point(aes(color = priceRange), alpha = 0.5) +
  geom_point(aes(x = center['x'], y = center['y']), color = "red")

ggplot(train, aes(longitude, latitude)) +
  geom_point(aes(color = city))
```

Price looks concentric.  Maybe add a distance to center?

```{r}
center <- train |> 
  filter(priceRange == "650000+") |> 
  select(longitude, latitude) |> 
  summarize(x = mean(longitude),
            y = mean(latitude)) |> 
  unlist()

train |> 
  mutate(dist = (longitude - center["x"])^2 + (latitude - center['y'])^2) |> 
  plot_price_curves(dist)
```

Looks reasonable.

```{r}
ggplot(train, aes(MedianStudentsPerTeacher, avgSchoolRating)) +
  geom_jitter(aes(color = priceRange), alpha = 0.5)

train |> 
  mutate(weird = (priceRange == "650000+") & (avgSchoolRating < 5)) |> 
  ggplot(aes(longitude, latitude)) +
  geom_point(aes(color = weird), alpha = 0.5)
```

Definite predictability.

```{r}
library(stopwords)

train |> 
  unnest_tokens(word, description) |> 
  anti_join(stop_words) |> 
  group_by(word, hi) |> 
  count() |> 
  filter(n >= 100) |> 
  ungroup(hi) |> 
  mutate(p = (n + 1)/(sum(n) + 1)) |> 
  filter(hi) |> 
  arrange(-p) |> 
  View()

train |> 
  filter(str_detect(description, "2016")) |> 
  select(description, priceRange)
```



