```{r}
library(tidyverse)
library(tidymodels)
library(forcats)
library(lubridate)
library(skimr)
library(corrr)
library(GGally)
library(fpp3)
```

```{r}
set.seed(80085)

df <- read_csv("2021-07/train.csv") %>%
  mutate(
    target_carbon_monoxide = log1p(target_carbon_monoxide),
    target_benzene = log1p(target_benzene),
    target_nitrogen_oxides = log1p(target_nitrogen_oxides)
  )
split <- initial_split(df)
train <- training(split)
test <- testing(split)
folds <- vfold_cv(train, v = 5)

mset <- metric_set(rmse)
grid_control <- control_grid(
  save_pred = TRUE,
  save_workflow = TRUE,
  verbose = TRUE
)
```

```{r}
summary(train$date_time)

train |> 
  filter(date_time <= ymd("2010-06-30"),
         date_time >= ymd("2010-05-01")) |> 
  pivot_longer(-date_time, names_to = "target", values_to = "val") |>
```


```{r}
ggplot(aes(date_time, val)) +
  geom_line() +
  facet_grid(rows = vars(target), scales = "free_y")
```


```{r}
train <- train %>%
  mutate(cluster = sensor_4 < 200 + sensor_1 / 2)

train %>% 
  mutate(hour = (hour + 20) %% 24) %>% 
  pivot_longer(starts_with("target"), names_to = "type", values_to = "val") %>% 
  group_by(weekend = day %in% c(0,6), hour, type) %>% 
  mutate(mean = mean(val)) %>% 
  ggplot(aes(hour, mean)) +
  geom_line(aes(color = weekend)) +
  facet_grid(rows = vars(type), scales = 'free_y')
```



```{r}
rec <- recipe(target_benzene ~ hour, data = train) %>% 
  step_mutate(hour = (hour + 20) %% 24) %>% 
  step_ns(hour, deg_free = 4)

rec %>% 
  prep() %>% 
  juice()

model <- linear_reg() %>% 
  set_engine('lm')

workflow() %>% 
  add_recipe(rec) %>% 
  add_model(model) %>% 
  fit(train) %>% 
  augment(train) %>% 
  group_by(hour) %>% 
  summarize(mean = mean(target_benzene),
            pred = mean(.pred)) %>% 
  ggplot(aes(x = hour)) +
  geom_line(aes(y = mean), color = 'blue') +
  geom_line(aes(y = pred), color = 'red')
```



```{r}
skim(train)
```

```{r}
rmses <- c(sd(train$target_benzene), sd(train$target_carbon_monoxide), sd(train$target_nitrogen_oxides))
rmses
mean(rmses)
```

### Naive score: 0.693
### RMSEs: Benzene - 0.76, CO - 0.43, NO - 0.88

```{r}
train %>%
  select(starts_with("sensor"), deg_C, relative_humidity, absolute_humidity, starts_with("target")) %>%
  ggpairs()
```

## One feature for when sensors might be off: sensor_4 < 200 + sensor_1/2

```{r}
train %>%
  ggplot(aes(sensor_1, sensor_4)) +
  geom_point(aes(color = target_carbon_monoxide)) +
  geom_abline(intercept = 200, slope = 0.5)

train <- train %>%
  mutate(cluster = sensor_4 < 200 + sensor_1 / 2)

train %>%
  ggplot(aes(sensor_2, cluster)) +
  geom_jitter()

train %>%
  ggplot(aes(absolute_humidity, target_carbon_monoxide)) +
  geom_point(aes(color = cluster))

train %>%
  ggplot(aes(sensor_2, target_benzene)) +
  geom_point(aes(color = cluster))
```

### Seems like humidities might be better when sensors are off

```{r}
train %>%
  filter(cluster == TRUE) %>%
  select(-date_time, -cluster) %>%
  ggpairs()
```

```{r}
train %>%
  filter(cluster == TRUE) %>%
  group_by(as_date(date_time)) %>%
  count()
```

```{r}
train %>% 
  select(date_time) %>% 
  mutate(hour = hour(date_time))

train %>%
  mutate(dow = wday(date),
         hour = (hour(date_time) + 18) %% 24) %>% 
  group_by(hour) %>%
  # group_by(date) %>%
  summarize(
    mean_b = mean(target_benzene),
    mean_n = mean(target_nitrogen_oxides),
    mean_c = mean(target_carbon_monoxide),
    # mean_p = mean(cluster)
  ) %>% 
  pivot_longer(starts_with("mean"), names_to = "type", values_to = "val") %>%
  ggplot(aes(hour, val)) +
  geom_line() +
  facet_grid(rows = vars(type), scales = "free_y")

train %>% 
  as_tsibble(index = date_time) %>%
  filter(month(date_time) %in% 5) %>% 
  mutate(`5-MA` = slider::slide_dbl(target_benzene, mean,
                .before = 24, .after = 0, .complete = TRUE)) %>% 
  autoplot(`5-MA`)
```




## Carbon_monoxide

```{r}
train %>%
  ggplot(aes(sensor_2, sensor_5)) +
  geom_point(aes(color = cluster))

train %>%
  ggplot(aes(sensor_1, sensor_4)) +
  geom_point(aes(color = target_carbon_monoxide)) +
  geom_abline(intercept = 200, slope = 0.5)

train %>%
  pivot_longer(c(starts_with("sensor"), deg_C, ends_with("humidity")), names_to = "sensor", values_to = "val") %>%
  ggplot(aes(val, target_carbon_monoxide)) +
  geom_point(aes(color = cluster)) +
  facet_wrap(vars(sensor), scales = "free_x")

train %>%
  filter(cluster == 1) %>%
  pivot_longer(c(starts_with("sensor"), deg_C, ends_with("humidity")), names_to = "sensor", values_to = "val") %>%
  ggplot(aes(val, target_carbon_monoxide)) +
  geom_point() +
  facet_wrap(vars(sensor), scales = "free_x")
```

```{r}
carbon_sens_rec <- recipe(target_carbon_monoxide ~ sensor_1 + sensor_2 + sensor_3 + sensor_4 + sensor_5, data = train) %>%
  step_filter(sensor_4 > 200 + sensor_1 / 2)

carbon_model <- linear_reg() %>%
  set_engine("lm")

carbon_sens_workflow <- workflow() %>%
  add_recipe(carbon_sens_rec) %>%
  add_model(carbon_model)

res <- carbon_sens_workflow %>%
  fit_resamples(folds, metrics = mset, control = grid_control)

res %>%
  collect_metrics()
```

```{r}
carbon_sens_workflow %>%
  finalize_workflow(select_best(res, "rmse")) %>%
  fit(data = train) %>%
  augment(test) %>%
  with(rmse_vec(.pred, target_carbon_monoxide))
```

--- 0.430 Naive
--- 0.184 cluster 0 + every sensor

## Benzene

```{r}
train %>%
  ggplot(aes(sensor_2, target_benzene)) +
  geom_point()
```

```{r}
benzene_rec <- recipe(target_benzene ~ sensor_2 + sensor_3
  # + sensor_1 + sensor_4 + sensor_5
  ,
  data = train
) %>%
  step_log(sensor_2)

benzene_rec %>%
  prep() %>%
  juice() %>%
  ggplot(aes(sensor_2, target_benzene)) +
  geom_point()

benzene_model <- linear_reg() %>%
  set_engine("lm")

benzene_workflow <- workflow() %>%
  add_recipe(benzene_rec) %>%
  add_model(benzene_model)

res <- benzene_workflow %>%
  fit_resamples(folds, metrics = mset, control = grid_control)

res %>%
  collect_metrics()
```

```{r}
benzene_workflow %>%
  finalize_workflow(select_best(res, "rmse")) %>%
  fit(train) %>%
  augment(test) %>%
  with(rmse_vec(.pred, target_benzene))
```

- 0.106 --- Just sensor 2 with log transform
- 0.102 --- + sensor 3
- 0.102 --- + filter out bad cluster


```{r}
resids <- benzene_workflow %>%
  fit(train) %>%
  augment(train) %>%
  mutate(residual = target_benzene - .pred)

resids %>%
  select(-starts_with("target"), -sensor_2, -date_time) %>%
  correlate() %>%
  select(term, residual) %>%
  filter(!is.na(residual)) %>%
  mutate(term = fct_reorder(term, residual)) %>%
  ggplot(aes(residual, term)) +
  geom_col()

resids %>%
  ggplot(aes(sensor_3, residual)) +
  geom_point()
```

### Nitrogen oxides

```{r}
train %>%
  filter(cluster == 0) %>%
  pivot_longer(c(starts_with("sensor"), deg_C, ends_with("humidity")), names_to = "sensor", values_to = "val") %>%
  ggplot(aes(val, target_nitrogen_oxides)) +
  geom_point() +
  facet_wrap(vars(sensor), scales = "free_x")

doParallel::registerDoParallel(cores = 1)
```

```{r}
NO_sens_rec <- recipe(target_nitrogen_oxides ~ sensor_1 + sensor_2 + sensor_3 + sensor_4 + sensor_5
  + date_time +
  +relative_humidity + absolute_humidity + deg_C, data = train) %>%
  step_filter(sensor_4 > 200 + sensor_1 / 2) %>% 
  step_mutate(weekend = wday(date_time) %in% c(0,6)) %>% 
  step_mutate(sept = month(date_time) > 8) %>% 
  step_rm(date_time)

NO_model <- linear_reg() %>%
  set_engine("lm")

NO_xgboost_model <- boost_tree(mode = "regression", learn_rate = tune(), trees = tune(), mtry = tune()) %>%
  set_engine("xgboost")

NO_sens_workflow <- workflow() %>%
  add_recipe(NO_sens_rec) %>%
  add_model(NO_xgboost_model)

NO_res <- NO_sens_workflow %>%
  # fit_resamples(folds, metrics = mset, control = grid_control)
  tune_grid(folds, metrics = mset, control = grid_control, grid = crossing(
    learn_rate = c(0.1, 0.3, 0.03),
    mtry = c(2),
    trees = seq(100, 500, 50)
  ))
```

```{r}
autoplot(NO_res)
```

```{r}
NO_sens_workflow %>%
  finalize_workflow(select_best(NO_res, "rmse")) %>%
  fit(data = train) %>%
  augment(test) %>%
  with(rmse_vec(.pred, target_nitrogen_oxides))
```

--- 0.88 - Naive
--- 0.43 - lm + sensors
--- 0.392 - xgb sensors + tuned
--- 0.381 -     + everything tuned
--- 0.319 -     + date (tuned + mtry)


```{r}
holdout <- read_csv("2021-07/test.csv")
holdout <- benzene_workflow %>%
  fit(df) %>%
  augment(holdout) %>%
  rename(target_benzene = .pred)

holdout_sensor <- holdout %>% filter(sensor_4 > 200 + sensor_1 / 2)
holdout_no_sensor <- holdout %>%
  filter(sensor_4 <= 200 + sensor_1 / 2) %>%
  mutate(
    target_carbon_monoxide = mean(df$target_carbon_monoxide),
    target_nitrogen_oxides = mean(df$target_nitrogen_oxides)
  )
```

```{r}
NO_sensor_holdout <- NO_sens_workflow %>%
  finalize_workflow(select_best(NO_res, "rmse")) %>%
  fit(df) %>%
  augment(holdout_sensor) %>%
  rename(target_nitrogen_oxides = .pred)

final_sensor <- carbon_sens_workflow %>%
  fit(df) %>%
  augment(NO_sensor_holdout) %>%
  rename(target_carbon_monoxide = .pred)
```

```{r}
final <- bind_rows(final_sensor, holdout_no_sensor) %>%
  select(date_time, starts_with("target")) %>%
  mutate(
    target_benzene = expm1(target_benzene),
    target_carbon_monoxide = expm1(target_carbon_monoxide),
    target_nitrogen_oxides = expm1(target_nitrogen_oxides),
  )

final

final %>%
  write_csv("attempt2.csv")
```

```{r}
read_csv("2021-07/test.csv") %>%
  with(mean(sensor_4 < 200 + sensor_1 / 2))

train %>%
  with(mean(sensor_4 < 200 + sensor_1 / 2))
```





```{r}
train %>%
  filter(cluster == 1) %>%
  pivot_longer(c(starts_with("sensor"), deg_C, ends_with("humidity")), names_to = "sensor", values_to = "val") %>%
  ggplot(aes(val, target_carbon_monoxide)) +
  geom_point() +
  facet_wrap(vars(sensor), scales = "free_x")

train %>%
  filter(cluster == 1) %>%
  select(-target_benzene, -target_nitrogen_oxides, -date_time, -cluster) %>%
  correlate() %>%
  select(term, target_carbon_monoxide) %>%
  head(8) %>%
  mutate(term = fct_reorder(term, target_carbon_monoxide)) %>%
  ggplot(aes(target_carbon_monoxide, term)) +
  geom_col()

sd(train %>% filter(cluster == 1) %>% pull(target_carbon_monoxide))

train %>%
  filter(cluster == 1) %>%
  ggplot(aes(relative_humidity, absolute_humidity)) +
  geom_point(aes(color = target_carbon_monoxide))
```

```{r}
carbon_no_rec <- recipe(target_carbon_monoxide ~ sensor_1 + sensor_4, data = train) %>%
  step_filter(sensor_4 <= 200 + sensor_1 / 2) %>%
  step_rm(sensor_1, sensor_4)

carbon_model <- linear_reg() %>%
  set_engine("lm")

carbon_xgboost_model <- boost_tree(mode = "regression", learn_rate = tune(), trees = tune()) %>%
  set_engine("xgboost")

carbon_no_workflow <- workflow() %>%
  add_recipe(carbon_no_rec) %>%
  # add_model(carbon_xgboost_model)
  add_model(carbon_model)

res <- carbon_no_workflow %>%
  fit_resamples(folds, metrics = mset, control = grid_control)
# tune_grid(folds, metrics = mset, control = grid_control, grid = crossing(
#   learn_rate = c(0.003, 0.01),
#   trees = seq(50, 400, 50)
# ))

res %>%
  collect_metrics()
```

```{r}
autoplot(res)
```

```{r}
carbon_no_workflow %>%
  finalize_workflow(select_best(res, "rmse")) %>%
  fit(data = train)
```

```{r}
carbon_no_workflow %>%
  finalize_workflow(select_best(res, "rmse")) %>%
  fit(data = train) %>%
  augment(test) %>%
  with(rmse_vec(.pred, target_carbon_monoxide))
```

--- 0.443 cluster 0 + Naive (no improvments otherwise)
