```{r}
library(tidyverse)
library(tidymodels)
library(skimr)
library(visdat)
library(here)
library(GGally)
library(lubridate)
```

```{r}
parks <- read_csv(here("data", "park_dimensions.csv")) |> 
  pivot_longer(contains("F_"), names_to = "name", values_to = "length") |>
  mutate(
    bearing = case_when(
      str_detect(name, "LF") ~ "left",
      str_detect(name, "RF") ~ "right",
      str_detect(name, "CF") ~ "center",
      TRUE ~ name
    ),
    type = str_match(name, "\\w\\w_(.*)")[, 2]
  ) |>
  select(-name, -Cover, -NAME) |> 
  group_by(park, bearing) |> 
  pivot_wider(c("park", "bearing"), names_from = "type", values_from = "length")
```

```{r}
df <- read_csv(here("data", "train.csv")) |>
  mutate(is_home_run = as.logical(is_home_run)) |>
  left_join(parks, by = "park")

df |> 
  mutate(na = is.na(launch_speed)) |> 
  chisq_test(is_home_run ~ na)

df |> 
  group_by(is.na(launch_angle)) |> 
  summarize(mean(is_home_run))
```


```{r}
set.seed(8291)
split <- initial_split(df, strata = "is_home_run")
train <- training(split)
```

```{r}
skim(train)
vis_miss(train)
```

5.29% HR: Need to handle class imbalance?

```{r}
train |>
  summarize(mean(is.na(launch_speed) | is.na(launch_angle)))
```

44.1% rows missing data from launch

```{r}
summarize_hr <- function(df, ...) {
  df |>
    group_by(...) |>
    summarize(
      mean = mean(is_home_run),
      n = n(),
      hr = sum(is_home_run)
    )
}
```


```{r}
train |>
  summarize_hr(bb_type)
```

Only fly balls and line drives are homeruns (with fly ball twice as likely)

```{r}
train |>
  filter(bb_type %in% c("fly_ball", "line_drive")) |>
  select(starts_with("launch")) |>
  vis_miss()
```

Still a lot of missing data.  Let's just look at fly balls and line_drives

```{r}
train <-
  train |>
  filter(bb_type %in% c("fly_ball", "line_drive"))
```


# Pure isolated characteristics

```{r}
launches <- train |>
  select(starts_with("launch"), is_home_run)

launches |>
  pivot_longer(-is_home_run, names_to = "term", values_to = "val") |>
  ggplot(aes(val)) +
  geom_density(aes(fill = as.factor(is_home_run)), alpha = 0.5) +
  facet_grid(rows = vars(term))

launches |>
  ggplot(aes(launch_speed, launch_angle)) +
  geom_point(aes(color = is_home_run))

launches |>
  mutate(
    v = launch_speed * sin(launch_angle * pi / 180),
    h = launch_speed * cos(launch_angle * pi / 180)
  ) |>
  ggplot(aes(h, v)) +
  geom_point(aes(color = is_home_run))

launches |>
  mutate(dist = launch_speed^2 * sin(launch_angle * pi / 180) * cos(launch_angle * pi / 180)) |>
  ggplot(aes(dist)) +
  geom_density(aes(fill = as.factor(is_home_run)), alpha = 0.5)

launches |>
  ggplot(aes(launch_speed)) +
  geom_density(aes(fill = as.factor(is_home_run)), alpha = 0.5)

launches |>
  ggplot(aes(launch_angle)) +
  geom_density(aes(fill = as.factor(is_home_run)), alpha = 0.5)
```


```{r}
delta_df <- train |> 
  mutate(
    dist = launch_speed^2 * sin(launch_angle * pi / 180) * cos(launch_angle * pi / 180) * 0.44704^2 * 2 / 9.8,
    delta = dist - Dim * 0.3048
  )

delta_df |> 
  filter(dist > 0, bb_type %in% c("fly_ball", "line_drive")) |> 
  summarize(mean(is_home_run))

delta_df |> 
  ggplot(aes(delta)) +
  geom_density(aes(fill = as.factor(is_home_run)), alpha = 0.5) +
  facet_wrap(~bearing)

delta_df |>
  filter(!is.na(delta)) |> 
  glm(formula = is_home_run ~ delta + bearing, family = "binomial") |> 
  summary()

delta_df |> 
  mutate(is_home_run = as.logical(is_home_run)) |> 
  select(is_home_run, delta, bearing) |> 
  distinct(is_home_run, bearing)
```

Probably don't need trigonometric transforms

```{r}
train |>
  ggplot(aes(plate_x, plate_z)) +
  geom_point(aes(color = is_home_run), alpha = 0.2)

train |>
  pivot_longer(c("plate_x", "plate_z"), names_to = "term", values_to = "val") |>
  ggplot(aes(val)) +
  geom_density(aes(fill = as.factor(is_home_run)), alpha = 0.5) +
  facet_grid(rows = vars(term), scales = "free_x")

t.test(train |> filter(is_home_run) |> pull(plate_z), train |> filter(!is_home_run) |> pull(plate_z))

t.test(train |> filter(is_home_run) |> pull(plate_x), train |> filter(!is_home_run) |> pull(plate_x))
```

Z position of plate matters, but X doesn't seem to.

```{r}
train |>
  summarize_hr(bearing)
```

Huge differences

```{r}
train |>
  ggplot(aes(pitch_mph)) +
  geom_density(aes(fill = is_home_run), alpha = 0.5)

train |>
  summarize_hr(pitch_name) |>
  mutate(
    pitch_name = fct_reorder(pitch_name, mean),
    lo = qbeta(0.025, hr + 1 / 2, n - hr + 1 / 2),
    hi = qbeta(0.975, hr + 1 / 2, n - hr + 1 / 2)
  ) |>
  ggplot(aes(mean, pitch_name)) +
  geom_point(aes(size = n)) +
  geom_errorbarh(aes(xmin = lo, xmax = hi), height = 0.5)


train |>
  ggplot(aes(pitch_mph)) +
  geom_density(aes(fill = is_home_run), alpha = 0.5) +
  facet_wrap(~pitch_name)
```

Different pitch types matter.  Speed seems to matter for knuckle curve, curve, and cutter.

```{r}
train |>
  group_by(is_batter_lefty, is_pitcher_lefty) |>
  summarize(
    mean = mean(is_home_run),
    n = n()
  ) |>
  ggplot(aes(is_batter_lefty, mean)) +
  geom_col(aes(fill = as.logical(is_pitcher_lefty)), position = "dodge")


train |>
  group_by(is_batter_lefty, is_pitcher_lefty) |>
  summarize(
    mean = mean(is_home_run),
    n = n()
  )
```

Righty batters are more likely to hit homeruns.
Righty pitchers are more likely to throw homeruns.

```{r}
train |>
  pivot_longer(cols = inning:strikes, names_to = "term", values_to = "val") |>
  summarize_hr(term, val) |>
  ggplot(aes(val, mean)) +
  geom_col() +
  geom_hline(yintercept = 0.0529, color = "red") +
  facet_grid(rows = vars(term), scales = "free")
```

Clear decrease when there are more outs and strikes.
Increase when there are more balls.
Some slight pattern on innings.

```{r}
train |>
  summarize_hr(month(game_date)) |>
  rename(month = `month(game_date)`) |>
  ggplot(aes(month, mean)) +
  geom_col()
```

```{r}
train |>
  mutate(is_home = home_team == batter_team) |>
  summarize_hr(is_home)

train |>
  mutate(home = home_team == batter_team) |>
  chisq_test(is_home_run ~ home)
```

Being the home team seems to help a little in the number of home runs


Huge spike in October

# Players

```{r}
batters <- train |>
  summarize_hr(batter_name, batter_id)

batters |>
  ggplot(aes(n)) +
  geom_density()

batters |>
  ggplot(aes(mean)) +
  geom_density()

batters |>
  filter(mean < 0.25) |>
  ggplot(aes(n, mean)) +
  geom_point() +
  geom_smooth()

batters |>
  filter(n > 50) |>
  arrange(-mean)

pitchers <- train |>
  summarize_hr(pitcher_name, pitcher_id)

pitchers |>
  ggplot(aes(n)) +
  geom_density()

pitchers |>
  ggplot(aes(mean)) +
  geom_density()

pitchers |>
  filter(mean < 0.5) |>
  ggplot(aes(n, mean)) +
  geom_point() +
  geom_smooth()

pitchers |>
  filter(n > 50) |>
  arrange(-mean)
```

# Parks

```{r}
library(broom)
train |>
  summarize_hr(NAME) |>
  arrange(-mean)

aov(is_home_run ~ Cover, data = train) |>
  summary()

train |>
  pivot_longer(ends_with("Dim")) |>
  ggplot(aes(value)) +
  geom_density(aes(fill = is_home_run), alpha = 0.5) +
  facet_grid(rows = vars(name), scales = "free")


train |>
  pivot_longer(ends_with("W")) |>
  ggplot(aes(value)) +
  geom_density(aes(fill = is_home_run), alpha = 0.5) +
  facet_grid(rows = vars(name), scales = "free")
```
