```{r}
library(tidyverse)
library(tidymodels)
library(lubridate)
library(forcats)
library(corrr)
library(skimr)

doParallel::registerDoParallel(cores = 2)
```

```{r}
df <- read_csv("train.csv") %>%
  mutate(
    date = ymd(date),
    del_humid = humidity3pm - humidity9am,
    del_wind = wind_speed3pm - wind_speed9am,
    del_cloud = cloud3pm - cloud9am,
    del_temp = temp3pm - temp9am,
    del_pressure = pressure3pm - pressure9am
  )
split <- initial_split(df)
train <- training(split)
test <- testing(split)
```

```{r}
mset <- metric_set(mn_log_loss)

(p <- train %>%
  pull(rain_tomorrow) %>%
  mean())

-p * log(p) - (1 - p) * log(1 - p)
```

```{r}
skim(train)
```

### Naive: p = 0.222, logloss - 0.529

```{r}
train %>%
  select(-id) %>%
  select_if(\(x) is.numeric(x) | is.logical(x)) %>%
  correlate() %>%
  select(term, rain_tomorrow) %>%
  mutate(term = fct_reorder(term, rain_tomorrow)) %>%
  filter(!is.na(rain_tomorrow)) %>%
  ggplot(aes(rain_tomorrow, term)) +
  geom_col()

train %>%
  select(-id) %>%
  select_if(\(x) is.numeric(x) | is.logical(x)) %>%
  correlate() %>%
  shave() %>%
  pivot_longer(!term, names_to = "term1", values_to = "val") %>%
  filter(!is.na(val)) %>%
  mutate(inter = fct_reorder(paste0(term, "-", term1), val)) %>%
  arrange(desc(abs(val))) %>%
  head(30) %>%
  ggplot(aes(val, inter)) +
  geom_col()
```

Temps are pretty correlated.  Delta-temp seems important and uncorrelated with temps

### Numericals

- Positive (most to least): Humidity 3pm, clouds, rain_today, humidity 9am, windgust
- Negative (most to least): Pressure, temp, maxtemp, sunshine, evap


```{r}
train %>%
  count(rain_today, rain_tomorrow) %>%
  pivot_wider(rain_today, names_from = rain_tomorrow, values_from = n)

train %>%
  count(rain_today, rain_tomorrow) %>%
  ggplot(aes(rain_tomorrow, n)) +
  geom_col() +
  facet_wrap(~rain_today, scale = "free")
```

```{r}
train %>%
  filter((rain_today == 0) & (rainfall > 0))
```

```{r}
compute_probs <- function(df, ...) {
  df %>%
    group_by(...) %>%
    summarize(
      mean = mean(rain_tomorrow),
      n = n()
    )
}
```


```{r}
train %>%
  ggplot(aes(x = humidity3pm, y = ..density..)) +
  geom_freqpoly(aes(color = as.factor(rain_tomorrow)))

train %>%
  group_by(humidity3pm, rain_tomorrow) %>%
  summarize(n = n()) %>%
  mutate(pct = n / sum(n)) %>%
  ggplot(aes(x = humidity3pm, y = pct)) +
  geom_area(aes(fill = as.factor(rain_tomorrow)))

train %>%
  mutate(delta_humid = floor((humidity3pm - humidity9am) / 5)) %>%
  compute_probs(delta_humid) %>%
  ggplot(aes(delta_humid, mean)) +
  geom_point(aes(size = n))

train %>%
  mutate(delta_humid = humidity3pm - humidity9am) %>%
  glm(formula = rain_tomorrow ~ delta_humid + humidity3pm, family = "binomial") %>%
  summary()

train %>%
  mutate(humidity3pm = floor(humidity3pm / 5)) %>%
  compute_probs(humidity3pm) %>%
  ggplot(aes(humidity3pm, mean)) +
  geom_point(aes(size = n))
```

- Humidity is highly predictive

```{r}
train %>%
  compute_probs(cloud3pm) %>%
  ggplot(aes(cloud3pm, mean)) +
  geom_point(aes(size = n))
```

- Clouds are also predictive

```{r}
train %>%
  compute_probs(wind_speed3pm) %>%
  ggplot(aes(wind_speed3pm, mean)) +
  geom_point(aes(size = n)) +
  geom_smooth(method = "lm")

train %>%
  compute_probs(wind_gust_speed) %>%
  ggplot(aes(wind_gust_speed, mean)) +
  geom_point(aes(size = n))
```

- Windspeed a little predictive

```{r}
train %>%
  ggplot(aes(del_temp)) +
  geom_histogram()

train %>%
  mutate(del_temp = floor(del_temp / 3)) %>%
  compute_probs(del_temp) %>%
  ggplot(aes(del_temp, mean)) +
  geom_point(aes(size = n))

train %>%
  ggplot(aes(del_temp, y = ..density..)) +
  geom_freqpoly(aes(color = as.factor(rain_tomorrow)))

train %>%
  with(cor(temp3pm, temp3pm, use = "complete.obs"))
```

- del_temp is not correlated and predictive

### Date

```{r}
train %>%
  mutate(month = month(date)) %>%
  compute_probs(month) %>%
  ggplot(aes(month, mean)) +
  geom_line()

train %>%
  mutate(
    month = month(date),
    year = year(date)
  ) %>%
  compute_probs(month, year) %>%
  group_by(month) %>%
  summarize(
    q50 = median(mean),
    q25 = quantile(mean, 0.25),
    q75 = quantile(mean, 0.75)
  ) %>%
  pivot_longer(!month, names_to = "type", values_to = "val") %>%
  ggplot(aes(month, val)) +
  geom_line(aes(color = type))


train %>%
  mutate(year = year(date)) %>%
  compute_probs(year) %>%
  ggplot(aes(year, mean)) +
  geom_point(aes(size = n))

train %>%
  mutate(
    year = year(date),
    month = month(date)
  ) %>%
  compute_probs(month, year) %>%
  group_by(year) %>%
  summarize(
    q50 = median(mean),
    q25 = quantile(mean, 0.25),
    q75 = quantile(mean, 0.75)
  ) %>%
  pivot_longer(!year, names_to = "type", values_to = "val") %>%
  ggplot(aes(year, val)) +
  geom_line(aes(color = type))
```

- Month probably useful (nonlinear).  Year, not so much

### Categoricals

```{r}
train %>%
  ggplot(aes(wind_dir3pm)) +
  geom_bar(aes(y = ..prop.., group = 1)) +
  facet_grid(row = vars(rain_tomorrow), scales = "free")

train %>%
  with(table(rain_tomorrow, wind_dir3pm)) %>%
  chisq.test()
```

```{r}
train %>%
  count(location) %>%
  ggplot(aes(n)) +
  geom_histogram()

train %>%
  group_by(location) %>%
  summarize(p = mean(rain_tomorrow), n = n(), sd = sd(rain_tomorrow)) %>%
  ggplot(aes(n, p)) +
  geom_point(aes(size = sd)) +
  geom_hline(yintercept = 0.222, color = "red")
```


### Model building

```{r}
train_fac <- train %>% mutate(rain_tomorrow = as.factor(rain_tomorrow))
train_folds <- vfold_cv(train_fac, v = 10)

lin_rec <- recipe(rain_tomorrow ~ min_temp + max_temp + wind_gust_speed + wind_speed9am + wind_speed3pm + humidity9am + humidity3pm + pressure9am + pressure3pm + cloud9am + cloud3pm + temp9am + temp3pm + rain_today, data = train) %>%
  step_impute_mean(all_numeric_predictors())
```

```{r}
lin_model <- logistic_reg() %>%
  set_engine("glm")

lin_workflow <- workflow() %>%
  add_recipe(lin_rec) %>%
  add_model(lin_model)

res <- lin_workflow %>%
  fit_resamples(train_folds, metrics = mset)
# grid= crossing(penalty=10^ seq(-7,-.5,.1)))

res %>% collect_metrics()
```

```{r}
fitted <- lin_workflow %>%
  fit(train_fac)

mn_log_loss_vec(as_factor(test$rain_tomorrow), predict(fitted, test, type = "prob")$.pred_0)
```

```{r}
xgb_model <- boost_tree(mode = "classification", trees = tune(), learn_rate = tune()) %>%
  set_engine("xgboost")

res <- workflow() %>%
  add_recipe(lin_rec) %>%
  add_model(xgb_model) %>%
  tune_grid(train_folds, metrics = mset, grid = crossing(trees = c(10, 20, 50),
                                                         learn_rate = c(0.01,0.03,0.1)))
```

```{r}
res %>% autoplot()
```
