Numeric:

* age_upon_outcome: age of the animal when the outcome was determined

NEED TO PARSE

Categorical:

* animal_type: cat, dog, or ... something else
* breed: breed of the animal
* color: color of the animal
* sex: sex of the animal
* spay_neuter: whether the animal was spayed or neutered: intact or fixed

- Idea: Mix in breed, possible one hot

Datetime:

* date_of_birth: date of birth of the animal
* datetime: date and time when the outcome was determined

- Idea: Time of year during datetime

String:

* name: name of the animal

name has asterisk

Target:
* outcome_type: there are three possible outcomes: adoption, transfer, no outcome (euthanized, died); not present in test.csv

(Class preds)


```{r}
library(tidyverse)
library(tidymodels)
library(tidytext)
library(lubridate)
library(here)
library(skimr)
library(infer)
```

```{r}
df <- read_csv(here("data", "train.csv"))
```

```{r}
set.seed(2021)
split <- initial_split(df)

train <- training(split)
```

```{r}
skim(train)
```

### Animal type and breed

```{r}
train |> 
  count(animal_type)
```

```{r}
train |> 
  select(breed)
```

```{r}
train_breeds <- train |> 
  mutate(mix = str_detect(breed, "Mix"),
         breed = str_match(breed, "^(.*?)( Mix)?$")[,2]) |> 
  unnest_tokens(breed, breed, token = "regex", pattern = "/")
```

```{r}
train_breeds |> 
  count(breed) |> 
  arrange(-n) |> 
  mutate(cumsum = cumsum(n)/(sum(n))) |> 
  filter(cumsum < 0.75)
```

```{r}
train_breeds |> 
  unite(breed, c("animal_type", "breed"), sep='-') |> 
  mutate(breed = fct_lump_n(breed, n = 15)) |> 
  group_by(breed, outcome_type) |> 
  count() |> 
  ungroup(outcome_type) |> 
  mutate(n = n/(sum(n))) |> 
  ggplot(aes(n, outcome_type)) +
  geom_col() +
  facet_wrap(~breed)
```

Breeds matter and type definitely matters

```{r}
train_breeds |> 
  distinct(breed, animal_type) |> 
  count(breed) |> 
  arrange(-n)
```

```{r}
train_breeds |>
  filter(animal_type == "Other") |> 
  count(breed) |> 
  arrange(-n)

train_breeds |> 
  filter(animal_type == "Dog") |> 
  mutate(breed = fct_lump_n(breed, n = 15)) |> 
  group_by(breed, outcome_type) |> 
  count() |> 
  ungroup(outcome_type) |> 
  mutate(n = n/(sum(n))) |> 
  ggplot(aes(n, outcome_type)) +
  geom_col() +
  facet_wrap(~breed)
```

* Dog breeds don't seem to matter much
* Cat breeds do


### Age

```{r}
train_age <- train |>
  separate(age_upon_outcome, c("age_num", "age_type"), sep = " ") |>
  mutate(
    age_num = as.integer(age_num),
    age_type = case_when(
      str_detect(age_type, "month") ~ 1 / 12,
      str_detect(age_type, "years") ~ 1,
      str_detect(age_type, "day") ~ 1 / 365,
      TRUE ~ 0
    ),
    age = age_num * age_type
  ) |> 
  select(-age_num, -age_type, -date_of_birth)
```

```{r}
train_age |> 
  filter(animal_type %in% c("Dog", "Cat")) |> 
  ggplot(aes(age)) +
  geom_density(aes(color = outcome_type)) +
  facet_grid(rows = vars(animal_type), scales = "free")
```


### Sex, Spay

```{r}
train |> 
  group_by(sex, animal_type, outcome_type) |> 
  count() |> 
  ungroup(outcome_type) |> 
  mutate(p = n / sum(n)) |> 
  ggplot(aes(p, outcome_type)) +
  geom_col(aes(fill = sex), position = "dodge") +
  facet_wrap(~animal_type)
```

```{r}
train |> 
  ggplot(aes(sex)) +
  geom_bar(aes(fill = outcome_type), position = 'fill') +
  facet_wrap(~animal_type)
```


```{r}
train |> 
  mutate(mix = str_detect(breed, "Mix")) |> 
  ggplot(aes(mix)) +
  geom_bar(aes(fill = outcome_type), position = 'fill') +
  facet_wrap(~animal_type)
```


People like female birds? and known sex other

```{r}
train |> 
  ggplot(aes(spay_neuter)) +
  geom_bar(aes(fill = outcome_type), position = 'fill') +
  facet_wrap(~animal_type)
```

People like fixed animals, especially for cats

```{r}
View(train)
```

```{r}
train |> 
  mutate(mix = str_detect(breed, "Mix")) |> 
  group_by(mix, outcome_type, animal_type) |> 
  count() |> 
  ungroup(outcome_type) |> 
  mutate(p = n / sum(n)) |> 
  ggplot(aes(p, outcome_type)) +
  geom_col(aes(fill = mix), position = "dodge") +
  facet_wrap(~animal_type, scales = 'free_x')
```

```{r}
train |> 
  filter(animal_type %in% c("Bird", "Cat", "Dog", "Other")) |> 
  mutate(month = month(datetime)) |> 
  group_by(animal_type, month, outcome_type) |> 
  count() |> 
  ungroup(outcome_type) |> 
  mutate(p = n/sum(n)) |> 
  ggplot(aes(month, p)) +
  geom_col() +
  facet_grid(rows=vars(animal_type), cols = vars(outcome_type), scales='free')
```

```{r}
train |> 
  filter(animal_type %in% c("Bird", "Cat", "Dog", "Other")) |> 
  mutate(aster = str_detect(name, "\\*")) |> 
  ggplot(aes(aster)) +
  geom_bar(aes(fill = outcome_type), position = "fill") +
  facet_wrap(~animal_type)
```









