---
title: "TidyTemplate"
date: 2021-07-27
output: html_output
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(broom)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-07-27")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

df <- tt$olympics
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
summer <- df |> 
  filter(season == "Summer") |> 
  select(-season, -games)

winter <- df |> 
  filter(season == "Winter") |>
  select(-season, -games)
```

```{r}
df |> 
  count(year) |> 
  arrange(year) |> 
  pull(year)

summer |>
  count(year) |> 
  arrange(year) |> 
  pull(year)

winter |> 
  count(year) |> 
  arrange(year) |> 
  pull(year)

df |>
  group_by(season, year) |> 
  summarize(num_countries = n_distinct(noc)) |> 
  ggplot(aes(year, num_countries)) +
  geom_line(aes(color = season))
```

```{r}
df |> 
  group_by(year, sex, season) |>
  summarize(n = n()) |> 
  ggplot(aes(year, n)) +
  geom_area(aes(fill = sex)) +
  facet_grid(rows = vars(season), scales = 'free_y')
```

```{r}
summer |> 
  group_by(noc) |>
  summarize(n = n_distinct(year)) |> 
  mutate(noc = fct_reorder(noc, n)) |>
  arrange(-n) |> 
  head(20) |> 
  ggplot(aes(n, noc)) +
  geom_col()
```

```{r}
summer |>
  filter(!is.na(medal), year >= 1948) |> 
  group_by(year, noc, event) |> 
  summarize(medals = n_distinct(medal)) |> 
  group_by(year, noc) |> 
  summarize(medals = sum(medals)) |> 
  group_by(noc) |>
  mutate(tot_medals = sum(medals)) |> 
  ungroup() |> 
  mutate(noc = fct_reorder(noc, tot_medals),
         noc = fct_lump_n(noc, w = tot_medals, n = 10)) |> 
  filter(noc != "Other") |> 
  ggplot(aes(year, medals)) +
  geom_line(aes(color = noc))

summer |> 
  group_by(year, noc) |> 
  summarize(medals = sum(!is.na(medal))) |> 
  group_by(noc) |> 
  mutate(tot_medals = sum(medals)) |> 
  ungroup() |> 
  mutate(noc = fct_reorder(noc, tot_medals),
         noc = fct_lump_n(noc, n = 10, w = tot_medals)) |> 
  filter(noc != "Other") |> 
  ggplot(aes(year, medals)) +
  geom_line(aes(color = noc))
```


```{r}
df |> 
  distinct(year, sport) |> 
  count(sport) |> 
  arrange(-n)

df |> 
  distinct(event, sport) |> 
  group_by(event) |> 
  count() |> 
  filter(n > 1)

df |> 
  filter(!is.na(medal)) |> 
  distinct(year, noc, sport, event, medal) |> 
  group_by(sport, noc) |> 
  summarize(n = n()) |> 
  group_by(sport) |> 
  mutate(total = sum(n),
         prop = n / total) |> 
  arrange(-prop) |> 
  filter(total >= 15)
```

```{r}
df <- df |> 
  filter(year >= 1948)

summer <- df |> 
  filter(season == "Summer") |> 
  select(-season, -games)

winter <- df |> 
  filter(season == "Winter") |>
  select(-season, -games)
```

```{r}
df |> 
  filter(!is.na(medal)) |> 
  distinct(year, noc, sport, event, medal) |> 
  group_by(sport, noc) |> 
  summarize(n = n()) |> 
  group_by(noc) |> 
  mutate(total = sum(n),
         prop = n / total) |> 
  slice_max(prop, n = 1) |> 
  filter(noc == "USA")
```

```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

df |> 
  filter(!is.na(medal)) |> 
  group_by(name, sex, noc) |> 
  summarize(n = length(medal),
         year = max(year),
         sport = getmode(sport)) |> 
  arrange(-n)

df |> 
  count(medal)

df |> 
  filter(!is.na(medal)) |> 
  group_by(name, sex, sport, noc) |> 
  summarize(
    gold = "Gold" %in% medal,
    tries = n(),
    year = max(year)
  ) |> 
  filter(!gold) |> 
  arrange(-tries)
```

```{r}
df |> 
  group_by(name, sex) |> 
  summarize(n = n_distinct(sport),
            sports = paste(unique(sport), collapse = ", "),
            country = getmode(noc),
            start = min(year),
            end = max(year)) |> 
  filter(n > 1) |> 
  arrange(-n) |> 
  View()

tibble(x = "a", y = 1:3) |> 
  group_by(x) |> 
  summarize(n = paste(distinct(., y)))

df |> 
  distinct(sport) |> 
  pull(sport)

df |> 
  distinct(sex)
```


```{r}
library(broom)

df |> 
  filter(!is.na(medal), !is.na(height), sex == "M") |>
  ggplot(aes(year, height)) +
  geom_jitter(alpha = 0.2) +
  geom_smooth()

df |> 
  filter(!is.na(medal), !is.na(height), sex == "F") |>
  ggplot(aes(year, height)) +
  geom_jitter(alpha = 0.2) +
  geom_smooth()

bad_sports <- df |> 
  distinct(year, sport) |> 
  count(sport) |> 
  filter(n < 3) |> 
  pull(sport)

reg_tbl <- df |> 
  filter(!is.na(medal),
         !is.na(height),
         !(sport %in% bad_sports),
         sex == "F") |> 
  nest(data = !sport) |> 
  bind_rows(df |> nest(data = everything()) |> mutate(sport = "All sports")) |> 
  mutate(reg = map(data, \(x) tidy(lm(height ~ year, data = x)))) |> 
  unnest(reg) |> 
  filter(term == "year")

reg_tbl |>
  filter(p.value <= 0.1) |> 
  mutate(sport = fct_reorder(sport, estimate)) |> 
  filter((abs(estimate) >= sort(abs(estimate), decreasing = TRUE)[19]) | sport == "All sports") |> 
  ggplot(aes(estimate, sport)) +
  geom_point() +
  geom_errorbarh(aes(xmin = estimate - 1.96 * std.error, xmax = estimate + 1.96 * std.error), height = 0.3)
```

```{r}
df |> 
  filter(sport == "Volleyball",
         sex == "F",
         !is.na(medal),
         year == 1992)

df |> 
  filter(sport == "Gymnastics",
         sex == "F",
         !is.na(medal)) |> 
  group_by(year) |> 
  summarize(height = mean(height, na.rm = TRUE)) |> 
  ggplot(aes(year, height)) +
  geom_line()
```


```{r}
reg_tbl <- df |> 
  filter(!is.na(height),
         !(sport %in% bad_sports),
         sex == "M") |> 
  nest(data = !sport) |> 
  bind_rows(df |> nest(data = everything()) |> mutate(sport = "All sports")) |> 
  mutate(regs = map(data, \(x) tidy(lm(height ~ year, data = x |> filter(is.na(medal))))),
         medalers = map(data, \(x) tidy(lm(height ~ year, data = x |> filter(!is.na(medal)))))) |> 
  unnest(c(regs, medalers), names_repair = "unique")

reg_tbl |> 
  select(sport, `term...3`, starts_with("estimate"), starts_with("std")) |> 
  filter(`term...3` == "year") |> 
  mutate(delta = `estimate...9` - `estimate...4`) |> 
  arrange(-abs(delta))

reg_tbl |>
  filter(p.value <= 0.1) |> 
  mutate(sport = fct_reorder(sport, estimate)) |> 
  filter((abs(estimate) >= sort(abs(estimate), decreasing = TRUE)[19]) | sport == "All sports") |> 
  ggplot(aes(estimate, sport)) +
  geom_point() +
  geom_errorbarh(aes(xmin = estimate - 1.96 * std.error, xmax = estimate + 1.96 * std.error), height = 0.3)
```

```{r}
df |> 
  filter(sex == "M", sport == "Trampolining") |> 
  mutate(medal = !is.na(medal)) |> 
  ggplot(aes(year, height)) +
  geom_point(aes(color = medal), alpha = 0.5)
```



# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
